Analysis

### 2020-01-10 analysis-cfa.Rmd
update0901-2020
Análisis Factorial de Escala actualizado con base de datos 09 enero 2020
commentarios primera versión

data01 <- sjlabelled::read_spss(path = "data/dat1.sav",verbose = FALSE)

@@

## Version 01:

@@

## Version 02:

@@

summary(fit2,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit2,what = "std")
```

## Version 03: orden aleatorio

@@

## Version 04: muestra completa

>>>>

data01 <- sjlabelled::read_spss(path = "data/Estudio_3_ola1_January_9_2020.sav",verbose = FALSE)

@@

## Version 01: Fixed order by perception / preferences (N=  )

@@

*summary*: good fit, heywood case item 8.

## Version 02: Fixed order, by topic (N=  )

@@

summary(fit2,standardized=TRUE, fit.measures=TRUE)
semPlot::semPaths(object = fit2,what = "std")
```
*summary*: bad fit, heywood

## Version 03: Random order

@@

*summary*: fit not very goood (RMSEA .7), no heywood. Try tau-equivalence

## Version 04: muestra completa (N=  )
